Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-10-12 manuscript/Chapter2-manuscript.Rmd
renamed files from chap3 to chap2

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

>>>>

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---
